---
title: "tms GeneHancer Demo: KLF1 enhancer/promoters"
output: html_document
css: style.css
---

### Overview

The principal goal here is to establish that TrenaMultiScore
containers, created in Seattle, work easily in Madison for Sirui.

There are two containers at present:

  - an RStudio server with some additional R libraries and this script
  - a Postgres database with version 5.16 of the GeneHancer data

They are linked together using docker-compose.

The demonstration here has only minor biological interest.  But
it serves to test our current goal: giving Sirui  extensible code
she can run.
```{r loadLibraries, echo=TRUE}
suppressWarnings(
   suppressMessages({
      library(ghdb)
      library(igvR)
      library(RPostgres)
      }))
```
Connect to the GeneHancer database, do a simple sanity check
```{r ghdbConnect, echo=TRUE}
gh <- DBI::dbConnect(RPostgres::Postgres(),
                     dbname = "ghdb",
                     host = "ghdb",
                     port = 5432,
                     user = "ghdb",
                     password="ghdb")
dbListTables(gh)

```
With ghdb connectivity established, we now query the database
for all the enhancers and promoters known, in relevant cell types,
for KLF1.

First we retrieve all tissues which have genehancer annotations.
We then select only those in celltype plausibly related to
erythropoisis, and query the database.
```{r queryKLF1 echo=TRUE}
   allTissues <- listTissues(ghdb, "KLF1")
   tissues <-   c(grep("myeloid", allTissues, ignore.case=TRUE, v=TRUE),
                  grep("eryth", allTissues, ignore.case=TRUE, v=TRUE),
                  grep("blood", allTissues, ignore.case=TRUE, v=TRUE))
   tbl <- retrieveEnhancersFromDatabase(ghdb, "KLF1", tissues)
   dim(tbl)
   checkTrue(nrow(tbl) >= 3)
   View(tbl)
```



